Fusion Moves for Correlation Clustering

### 2014-11-10 paper/inputs/fig_fusion.tex
mystuff

\begin{center}
\begin{figure}[ht]
\begin{tiny}

\begin{subfigure}[t]{0.7\linewidth}
    \resizebox{\linewidth}{!}{
        \begin{tikzpicture}[scale=1]%[x=1 cm, y=1 cm]

@@

                % 2. FUSION
                \draw (2+8,2) node[nS,fill=blue!60] (n0) {$0$}; 
                \draw (4+8,2) node[nS,fill=green!60] (n1) {$1$};
                \draw (2+8,0) node[nS,fill=blue!60] (n3) {$2$}; 
                \draw (4+8,0) node[nS,fill=green!60] (n4) {$3$};
                \path
                    (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                    (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                    (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                    (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
                ;

                \draw (2+8,2-4) node[nD, circle split part fill={red!60, blue!60}] (n0) {$ $}; 
                \draw (4+8,2-4) node[nD, circle split part fill={red!60, green!60}] (n1) {$ $};
                \draw (2+8,0-4) node[nD, circle split part fill={green!60, blue!60}] (n3) {$ $}; 
                \draw (4+8,0-4) node[nD, circle split part fill={green!60, green!60}] (n4) {$ $};
                \path
                    (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                    (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                    (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                    (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
                ;

                % 3. FUSION
                \draw (2+12,2) node[nS,fill=red!60] (n0) {$0$}; 
                \draw (4+12,2) node[nS,fill=blue!60] (n1) {$1$};
                \draw (2+12,0) node[nS,fill=red!60] (n3) {$2$}; 
                \draw (4+12,0) node[nS,fill=blue!60] (n4) {$3$};
                \path
                    (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                    (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                    (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                    (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
                ;

                \draw (2+12,2-4) node[nD, circle split part fill={red!60, red!60}] (n0) {$ $}; 
                \draw (4+12,2-4) node[nD, circle split part fill={red!60, blue!60}] (n1) {$ $};
                \draw (2+12,0-4) node[nD, circle split part fill={green!60, red!60}] (n3) {$ $}; 
                \draw (4+12,0-4) node[nD, circle split part fill={green!60, green!60}] (n4) {$ $};
                \path
                    (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                    (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                    (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                    (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
                ;

                % 4. FUSION
                \draw (2+16,2) node[nS,fill=magenta!60] (n0) {$0$}; 
                \draw (4+16,2) node[nS,fill=blue!60] (n1) {$1$};
                \draw (2+16,0) node[nS,fill=magenta!60] (n3) {$2$}; 
                \draw (4+16,0) node[nS,fill=blue!60] (n4) {$3$};
                \path
                    (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                    (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                    (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                    (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
                ;

                \draw (2+16,2-4) node[nD, circle split part fill={red!60, magenta!60}] (n0) {$ $}; 
                \draw (4+16,2-4) node[nD, circle split part fill={red!60, blue!60}] (n1) {$ $};
                \draw (2+16,0-4) node[nD, circle split part fill={green!60, magenta!60}] (n3) {$ $}; 
                \draw (4+16,0-4) node[nD, circle split part fill={green!60, blue!60}] (n4) {$ $};
                \path
                    (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                    (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                    (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                    (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
                ;

        \end{tikzpicture}
    }
\caption{b}
\label{fig:f_b}
\end{subfigure}

\end{tiny}
\caption{
w
}\label{fig:fusion_abiguty}
\end{figure}
\end{center}

>>>>

\begin{center}
\begin{figure}[ht]
\resizebox{\linewidth}{!}{
    \begin{tikzpicture}[scale=1]%[x=1 cm, y=1 cm]

@@

            % 2. FUSION
            \draw (2+8,2) node[nS,fill=red!60] (n0) {$0$}; 
            \draw (4+8,2) node[nS,fill=blue!60] (n1) {$1$};
            \draw (2+8,0) node[nS,fill=red!60] (n3) {$2$}; 
            \draw (4+8,0) node[nS,fill=blue!60] (n4) {$3$};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+8,2-4) node[nD, circle split part fill={red!60, red!60}] (n0) {$ $}; 
            \draw (4+8,2-4) node[nD, circle split part fill={red!60, blue!60}] (n1) {$ $};
            \draw (2+8,0-4) node[nD, circle split part fill={green!60, red!60}] (n3) {$ $}; 
            \draw (4+8,0-4) node[nD, circle split part fill={green!60, green!60}] (n4) {$ $};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

            % 3. FUSION
            \draw (2+12,2) node[nS,fill=green!60] (n0) {$0$}; 
            \draw (4+12,2) node[nS,fill=red!60] (n1) {$1$};
            \draw (2+12,0) node[nS,fill=green!60] (n3) {$2$}; 
            \draw (4+12,0) node[nS,fill=red!60] (n4) {$3$};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+12,2-4) node[nD, circle split part fill={red!60, green!60}] (n0) {$ $}; 
            \draw (4+12,2-4) node[nD, circle split part fill={red!60, red!60}] (n1) {$ $};
            \draw (2+12,0-4) node[nD, circle split part fill={green!60, green!60}] (n3) {$ $}; 
            \draw (4+12,0-4) node[nD, circle split part fill={green!60, red!60}] (n4) {$ $};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

            % 4. FUSION
            \draw (2+16,2) node[nS,fill=green!60] (n0) {$0$}; 
            \draw (4+16,2) node[nS,fill=blue!60] (n1) {$1$};
            \draw (2+16,0) node[nS,fill=green!60] (n3) {$2$}; 
            \draw (4+16,0) node[nS,fill=blue!60] (n4) {$3$};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+16,2-4) node[nD, circle split part fill={red!60, green!60}] (n0) {$ $}; 
            \draw (4+16,2-4) node[nD, circle split part fill={red!60, red!60}] (n1) {$ $};
            \draw (2+16,0-4) node[nD, circle split part fill={green!60, green!60}] (n3) {$ $}; 
            \draw (4+16,0-4) node[nD, circle split part fill={green!60, red!60}] (n4) {$ $};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

            % 5. FUSION
            \draw (2+20,2) node[nS,fill=blue!60] (n0) {$0$}; 
            \draw (4+20,2) node[nS,fill=red!60] (n1) {$1$};
            \draw (2+20,0) node[nS,fill=blue!60] (n3) {$2$}; 
            \draw (4+20,0) node[nS,fill=red!60] (n4) {$3$};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+20,2-4) node[nD, circle split part fill={red!60, blue!60}] (n0) {$ $}; 
            \draw (4+20,2-4) node[nD, circle split part fill={red!60, red!60}] (n1) {$ $};
            \draw (2+20,0-4) node[nD, circle split part fill={green!60, blue!60}] (n3) {$ $}; 
            \draw (4+20,0-4) node[nD, circle split part fill={green!60, red!60}] (n4) {$ $};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

            % 6. FUSION
            \draw (2+24,2) node[nS,fill=blue!60] (n0) {$0$}; 
            \draw (4+24,2) node[nS,fill=green!60] (n1) {$1$};
            \draw (2+24,0) node[nS,fill=blue!60] (n3) {$2$}; 
            \draw (4+24,0) node[nS,fill=green!60] (n4) {$3$};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+24,2-4) node[nD, circle split part fill={red!60, blue!60}] (n0) {$ $}; 
            \draw (4+24,2-4) node[nD, circle split part fill={red!60, green!60}] (n1) {$ $};
            \draw (2+24,0-4) node[nD, circle split part fill={green!60, blue!60}] (n3) {$ $}; 
            \draw (4+24,0-4) node[nD, circle split part fill={green!60, green!60}] (n4) {$ $};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

            % 7. FUSION
            \draw (2+28,2) node[nS,fill=blue!60] (n0) {$0$}; 
            \draw (4+28,2) node[nS,fill=yellow!60] (n1) {$1$};
            \draw (2+28,0) node[nS,fill=blue!60] (n3) {$2$}; 
            \draw (4+28,0) node[nS,fill=yellow!60] (n4) {$3$};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+28,2-4) node[nD, circle split part fill={red!60, blue!60}] (n0) {$ $}; 
            \draw (4+28,2-4) node[nD, circle split part fill={red!60, yellow!60}] (n1) {$ $};
            \draw (2+28,0-4) node[nD, circle split part fill={green!60, blue!60}] (n3) {$ $}; 
            \draw (4+28,0-4) node[nD, circle split part fill={green!60, yellow!60}] (n4) {$ $};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

    \end{tikzpicture}
}
\caption{
w
}\label{fig:fusion_abiguty}
\end{figure}
\end{center}
